This chapter describes chosen theory that our group applied in our project.
\\\\
\textbf{Business Model Canvas}, BMC, was used to constitute the foundation of our cooperation with \textit{Aasted ApS} and the final business case. By examining \textit{Aasted ApS}, mainly through their website\footnote{http://wwww.aasted.eu}, we were able to complete our BMC. In our project, it was of vital importance, as it uncovered the value and purpose\footnote{\cite{osterwalder}, p. 14.} of \textit{Aasted ApS} prior to our first meeting.
\\\\
The BMC served as a guideline for our first meeting\footnote{Resume of meeting on the 13\textsuperscript{th} of September can be found in appendix \ref{meeting_13_9}.} with \textit{Aasted ApS} and their CEO, \textit{Piet Tæstensen}. This allowed us - at our very first meeting - to uncover the strategies, goals and IT circumstances of the organization as well as their current pains. With the help of some provided documentation, this meant that because of the BMC, we were able to cover most of the intiation and in-line phase in one meeting.
\\\\
\textbf{Interviews} was the primary MUST technique in our group, consequently conducted at \textit{Aasted ApS} in the interviewees respective department. The interviews were all conducted in the \textit{in-depth phase} for us to understand work processes, task, work functions, and issues regarding these. This gave us concrete experience with the interviewees work practices, IT usage and technological options (the knowledge areas D-F\footnote{\cite{boedker}, p. 200}).
\\\\
Immediately after an interview, we compared notes, consulting the recorded audio, if any disagreements arose concerning the context. Following the comparison, a summary was written, checking the recorded audio for any missed points. Lastly the summary was forwarded to the interviewee to confirm, comment and correct the content. This gave us concrete and confirmed data, which proved to be very helpful arguments in the form of diagnostic maps.
\iffalse
Our instant documentation and analysis of data forced us to examine and evaluate the data, while it was still fresh in our memory, allowing us to easily formulate future questions and actions with the \textit{Aasted ApS}.
\fi
\\\\
\textbf{Diagnostic Maps}
was used to identify issues, their cause, and their consequence\footnote{\cite{boedker}, p. 278}. We produced Diagnostic Maps for all interviews conducted in the Service department immediately after writing the summaries. At the end of the in-depth phase the mapping was then used to relate problems to our ideas for solutions. This constituted useful argumentation for the relevance of our proposed visions with the steering committee, effectively enforcing the  MUST principle anchoring visions\footnote{\cite{boedker}, p. 212}.
\\\\
\textbf{Observations}  complimented our interviews with first-hand experience of work practices, effectively helping us avoid the \textit{say-do problem}\footnote{\cite{boedker}, p. 246}. A \textit{passive observation}\footnote{\cite{boedker}, p. 210} was explicitly coordinated with the observed employees to avoid \textit{thinking-aloud}\footnote{\cite{boedker}, p. 210} behavior, which would hinder the detection of any \textit{say-do problems}. The observation was represented in a workflow diagram for an easier, more visual overview, than a summary - the proposed representation tool.